Sparse Function-space Representation \\ of Neural Networks

### 2023-05-23 paper/main.tex

\section{Method details}
\label{app:method}
%
Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
This section will often be part of the supplemental material.

>>>>

\section{Method details}
\label{app:method}
%
Key to our method is the ability to compute the dual parameters in \cref{eq:dual_param}. For general exponential family likelihoods we can derive simpler expressions:
\begin{equation}
 \ell(\sigma(f), y) = -\log p(y \mid f) =  A(f)  - \langle y, f\rangle
\end{equation}
where $A(f)$ is the log partition function and $\sigma(.)$ is the link function. Taking the first and second derivative of the loss in this form then become:

 For the Bernoulli distribution with a given link function, typically the sigmoid, $\sigma(f_{\vw}(\vx)):= \sigma(f) = \frac{1}{1+e^f}$. Then, we can write the log probability as
%\begin{equation}
%\begin{aligned}
%	\ell(y, \vf_\vw(\vx)) 
%%	&:= - \log p(y | \sigma(f))) \\
%%	&= -y \log(\sigma(f)) - (1-y) \log(1-\sigma(f))\\
%%	&= -y f + \log(1+e^f) \red{ \left[ = - (\langle f, y\rangle - \log(1+e^f)) \right] }
%\end{aligned}
%\end{equation}
